Generality in food webs scales with species richness, not latitude

### 2015-04-10 manuscript/latitudepaper.tex
Figure roundup

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
%\usepackage{rotating}
% make Figure 1 etc bold
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}

@@

  \begin{equation}
  \label{Latfull}
  S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} .,
  \end{equation}

@@

  \begin{equation}
  \label{Power}
  Z_{i} \~ \alpha S_{i}^{\beta} .,
  \end{equation}

@@

  \begin{equation}
  \label{Loglog}
  \log{Z_{i}} \~ \log{\alpha} + \beta\log{S_{i}} ..
  \end{equation}

@@

  \begin{equation}
  \label{PowerLat}
  Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} .,
  \end{equation}

@@

  \begin{equation}
  \label{LogLat}
  \log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i} ..
  \end{equation}

@@

% \begin{figure}[!h]
% \label{Latfigs}
% \includegraphics[width=.9\textwidth]{Figures/properties_vs_lat.eps}
% \caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability. No food web property showed a significant latitudinal gradient in this dataset (N=259 food webs).}
% \end{figure}

% \begin{figure}[!h]
% \label{scalingfig}
% \includegraphics[width=.9\textwidth]{Figures/nonts_scaling_with_S_grey.eps}
% \caption{Relationships between species richness and mean links per species, mean generality, and mean 
% vulnerability (N=259 food webs). Scaling of mean links per species and mean vulnerability with species 
% richness strengthened with latitude for estuarine, stream, and lake food webs. This strengthening was
% reversed for marine and terrestrial food webs. Scaling of mean generality with species richness 
% strengthened with latitude for lake food webs, but did not significantly vary with latitude for other
% ecosystem types (N=259 food webs). }
% \end{figure}

\begin{figure}[!h]
\label{props_v_lat}
\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_propsvlat.eps}
\caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability (N=163 food webs). }
\end{figure}

\begin{figure}[!h]
\label{TLs_v_lat}
\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_TLvlat.eps}
\caption{Relationships between latitude and proportions of basal resources, intermediate consumers, and top predators (N=163 food webs). }
\end{figure}

@@

\begin{figure}[!h]
\label{S}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
\caption{}
\end{figure}

\begin{figure}[!h]
\label{B}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
\caption{}
\end{figure}

\begin{figure}[!h]
\label{I}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/I_latlines_nonts.eps}
\caption{}
\end{figure}

\begin{figure}[!h]
\label{T}
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/T_latlines_nonts.eps}
\caption{}
\end{figure}

>>>>

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
%\usepackage{rotating}
% make Figure 1 etc bold
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}

@@

  \begin{equation}
  \label{Latfull}
  S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
  \end{equation}

@@

  \begin{equation}
  \label{Power}
  Z_{i} \sim \alpha S_{i}^{\beta}  ,
  \end{equation}

@@

  \begin{equation}
  \label{Loglog}
  \log{Z_{i}} \sim \log{\alpha} + \beta\log{S_{i}}  .
  \end{equation}

@@

  \begin{equation}
  \label{PowerLat}
  Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} ,
  \end{equation}

@@

  \begin{equation}
  \label{LogLat}
  \log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i} .
  \end{equation}

@@

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
\caption{Scaling of link density, generality, and vulnerability with species richness
varies across ecosystem types and over latitude. For each property we show 
prediction curves for food webs at the equator (darkest line) and at 
20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
equator. We did not include direction (i.e., North or South) in our analyses. 
All curves are based on N=163 empirical food webs.}
\label{S}
\end{figure}

\begin{figure}[!H]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
\caption{Scaling of link density, generality, and vulnerability 
with the proportion of basal resources in a food web
varies across ecosystem types and over latitude. For each property we show 
prediction curves for food webs at the equator (darkest line) and at 
20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
equator. We did not include direction (i.e., North or South) in our analyses. 
All curves are based on N=163 empirical food webs.}
\label{B}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/I_latlines_nonts.eps}
\caption{Scaling of link density, generality, and vulnerability 
with the proportion of intermediate consumers in a food web
varies across ecosystem types and over latitude. For each property we show 
prediction curves for food webs at the equator (darkest line) and at 
20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
equator. We did not include direction (i.e., North or South) in our analyses. 
All curves are based on N=163 empirical food webs.}
\label{I}
\end{figure}

\begin{figure}[h]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/T_latlines_nonts.eps}
\caption{Scaling of link density, generality, and vulnerability 
with the proportion of top predators in a food web
varies across ecosystem types and over latitude. For each property we show 
prediction curves for food webs at the equator (darkest line) and at 
20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
equator. We did not include direction (i.e., North or South) in our analyses. 
All curves are based on N=163 empirical food webs.}
\label{T}
\end{figure}

\begin{figure}[H]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) 
against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
predators (\% Top), and species richness of a food web. 
For each relationship we show observed values corrected for
ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). }
\label{props_v_lat}
\end{figure}
